Deriving Multi-Headed Projective Dependency Parses from Link Grammar Parses

### 2014-11-21 doc/LinksToDAG_final.tex
answered a couple more reviewer issues

Our objective tries to minimize the number of allowed directions (by link type---cf.\@ \newcite{ravi2009}) and the total slack (by link token):
\begin{align}\label{eqn:obj}
\min \left( \sum_{L} r_L + \ell_L \right) \cdot \frac{N_L}{4} + \sum_{ij} s_{ij}
\end{align}
where $N_L$ is the number of link tokens with label $L$.  Objective \eqnref{obj} is willing to tolerate up to 1/4 of those link tokens' using a disallowed direction before it prefers to allow {\em both} directions. \noteJE{check!}
% CUT FOR SPACE
% (i.e., $r_L+\ell_L=2$).

@@

The link grammar results in multi-headed treatments of infinitivals, compound determiners, relative clauses, and embedding.  The other annotation differences are generally reasonable, e.g., letting {\em 's} be the head of a possessive, and different handling of punctuation and lists.  Of course, a few of the differences are due to parser attachment errors.

>>>>

Our objective tries to minimize the number of allowed directions (by link type---cf.\@ \newcite{ravi2009}) and the total slack (by link token):
\begin{align}\label{eqn:obj}
\min \left( \sum_{L} r_L + \ell_L \right) \cdot \frac{N_L}{4} + \sum_{ij} s_{ij}
\end{align}
where $N_L$ is the number of link tokens with label $L$.  Objective \eqnref{obj} is willing to tolerate up to 1/4 of those link tokens' using a disallowed direction before it prefers to allow {\em both} directions. 
\noteJE{check!}
One could experiment with adjusting the constant 1/4; we selected that value simply because it seemed like a reasonable threshold {\em a priori}.
% CUT FOR SPACE
% (i.e., $r_L+\ell_L=2$).

@@

The link grammar results in multi-headed treatments of infinitivals, compound determiners, relative clauses, and embedding.  The other annotation differences are generally reasonable, e.g., letting {\em 's} be the head of a possessive, and different handling of punctuation and lists.  One could easily modify the ILP to explicitly encourage agreement with the CoNLL link directions (for word pairs that are linked in CoNLL).  Of course, a few of the differences are due to parser attachment errors.
